Manuscript

### 2021-01-19 Manuscript/Manuscript.Rmd
add important keywords in the first session results

@@

Subsequently, cycles of prediction/review tasks were performed, in which manually reviewed records (R tasks) were used to train the ML classification algorithm which is then used to reclassify all records (P tasks). After task 11, two susbsequent P tasks returned no uncertain or positive unreviewed predictions, therefore the first session was termined. In total `r task_table[['R']] - 1` review tasks were required in addition to the initial manual classification (tab. 1), for a total of `r sum(new_uncertains, new_positives)` extra reviewed articles (`r new_uncertains` predicted as uncertain and `r new_positives` as positive).\
Overall `r new_uncertains + new_positives + first_annotation_results$Reviewed` classification/review actions on `r all_unique_reviews` records were required, that is the `r percent((new_uncertains + new_positives + first_annotation_results$Reviewed)/sources_first_query$Total)` of the total number of records (`r sources_first_query$Total`) collected in the first session, while the rest was classified automatically as non-relevant.
The dataset at the end of the session contained a total of `r final_positives` positive records (+`r final_positives - first_annotation_results$Reviewed_positive` positive records compared to the initial manual classification).\
The ML algorithm showed a gradually improving out-of-bag performance, ranging from `r AUC_vec[1]` for the first predictive task to `r last(AUC_vec)` for the last, with the sensitivity always keeping an edge over the specificity, as per the model intentions.

>>>>

final_keywords <- annotation_summary %>% filter(Batch == first_batch & Label == 'Important_vars') %>% pull(Value) %>% last()

@@

Subsequently, cycles of prediction/review tasks were performed, in which manually reviewed records (R tasks) were used to train the ML classification algorithm which is then used to reclassify all records (P tasks). After task 11, two susbsequent P tasks returned no uncertain or positive unreviewed predictions, therefore the first session was termined. In total `r task_table[['R']] - 1` review tasks were required in addition to the initial manual classification (tab. 1), for a total of `r sum(new_uncertains, new_positives)` extra reviewed articles (`r new_uncertains` predicted as uncertain and `r new_positives` as positive).\
Overall `r new_uncertains + new_positives + first_annotation_results$Reviewed` classification/review actions on `r all_unique_reviews` records were required, that is the `r percent((new_uncertains + new_positives + first_annotation_results$Reviewed)/sources_first_query$Total)` of the total number of records (`r sources_first_query$Total`) collected in the first session, while the rest was classified automatically as non-relevant.
The dataset at the end of the session contained a total of `r final_positives` positive records (+`r final_positives - first_annotation_results$Reviewed_positive` positive records compared to the initial manual classification).\
The ML algorithm showed a gradually improving out-of-bag performance, ranging from `r AUC_vec[1]` for the first predictive task to `r last(AUC_vec)` for the last, with the sensitivity always keeping an edge over the specificity, as per the model intentions.\
The 15 most important keywords for the ML algorithm at the end of the session were: *`r final_keywords`*.
